Biomass trend maps

### 2019-07-13 analysis/VOCC/biomass-trends.Rmd
add any_rock substrate variable that combines rocky and mixed

# Choose covariates  
```{r}
covariates <- "+muddy+mixed+rocky"
covariates <- "+mixed+rocky"

covariates <- "+trawled+muddy+rocky+mixed"
covariates <- "+trawled+mixed+rocky"
covariates <- "+trawled+mixed"
```

@@

Make prediction grids for all surveys and years, if not done before.
```{r, message=FALSE, warning=FALSE}
try(nd_all <- readRDS("data/nd_all_synoptic.rds"))

@@

  newcov <- readRDS("data/new_covariates.rds") %>% dplyr::select(X, Y, trawled, muddy, rocky, mixed)
  nd_all <- left_join(nd_all, newcov, by=c("X", "Y"))

>>>>

# Choose covariates  
```{r}
covariates <- "+muddy+mixed+rocky"
covariates <- "+mixed+rocky"
covariates <- "+muddy+any_rock"

# covariates <- "+trawled+muddy+rocky+mixed"
# covariates <- "+trawled+mixed+rocky"
# covariates <- "+trawled+mixed"

@@

Make prediction grids for all surveys and years, if not done before.
```{r, message=FALSE, warning=FALSE}
#try(nd_all <- readRDS("data/nd_all_synoptic.rds"))

@@

  newcov <- readRDS("data/new_covariates.rds") %>% dplyr::select(X, Y, trawled, muddy, rocky, mixed, any_rock)
  nd_all <- left_join(nd_all, newcov, by=c("X", "Y"))
